Switch equivalence and weak prime domains for left-linear DPO rewriting systems

### 2025-02-20 full_version/adhesivity.tex
lavorato sulle permutazioni consistenti :^)))))))
minori

@@

\subsubsection{Pushout complements}

@@

\begin{corollary}\label{lem:radj} Let $\X$ be an $\mathcal{M}$-adhesive category and consider two composable arrows $m\colon M \mto X$  and $f\colon X\to Y$, with $m\in \mathcal{M}$. Suppose moreover that the following square is a pushout, so that $(h,k)$ is a pushout complement og $(m,f)$:
	\[\xymatrix{M \ar@{>->}[r]^{m}\ar[d]_{h}& X \ar[d]^{f} \\Q\ar@{>->}[r]_{k}&Y}\]

>>>>

\begin{remark}
	\label{rem:iso}
	Every category $\X$ is $\mathsf{I(\X)}$-adhesive, where $\mathsf{I(\X)}$ is the class of 
	isomorphisms.
\end{remark}

@@

\subsection{Pushout complements}

@@

\begin{corollary}\label{lem:radj} Let $\X$ be an $\mathcal{M}$-adhesive category and consider two composable arrows $m\colon M \mto X$  and $f\colon X\to Y$, with $m\in \mathcal{M}$. Suppose moreover that the following square is a pushout, so that $(h,k)$ is a pushout complement of $(m,f)$:
	\[\xymatrix{M \ar@{>->}[r]^{m}\ar[d]_{h}& X \ar[d]^{f} \\Q\ar@{>->}[r]_{k}&Y}\]
